---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# ussie

<!-- badges: start -->
[![R-CMD-check](https://github.com/NatalieWeaver/ussie/actions/workflows/R-CMD-check.yaml/badge.svg)](https://github.com/NatalieWeaver/ussie/actions/workflows/R-CMD-check.yaml)
[![test-coverage](https://github.com/NatalieWeaver/ussie/actions/workflows/test-coverage.yaml/badge.svg)](https://github.com/NatalieWeaver/ussie/actions/workflows/test-coverage.yaml)
<!-- badges: end -->

## Introduction

All of the students in the "Building Tidy Tools" workshop at rstudio::conf(2022) built `ussie` to learn package development. A huge thanks to Emma Rand and Ian Lyttle for being fantastic teachers.

Course materials:

* [Course website](https://rstudio-conf-2022.github.io/build-tidy-tools/)
* ["BT2T" course package](https://github.com/rstudio-conf-2022/btt22)
* [ussie example from instructors](https://github.com/rstudio-conf-2022/ussie)

The goal of `ussie` is to help you work with European soccer league data supplied by the `engsoccerdata` package. The name "ussie" is a reference to the Apple tv show "Ted Lasso".

## Installation

You can install the development version of ussie from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("NatalieWeaver/ussie")
```

## Example

This is a basic example which shows you how to solve a common problem:

```{r example}
library(ussie)
# get the England league data in standard format
uss_make_matches(engsoccerdata::england, "England")
```

